### 2023-11-23 main.tex
^'^

Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square bracket, that is non-vanishing only if $\sigma_{x}=\tau_{x}$. On the other hand, if $\sigma_{x}=N$ the quantity $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=1=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}$. \\

@@

Indeed: if $\tau_{x}=\sigma_{x}N$, both sides are $1$; if $\tau_{x}\neq N$ and $\sigma_{x}=N$ both sides are $\beta_{\tau_{x}}$; while, in all other cases, both sides are $0$. 

@@

We observe that the argument of the summation above does not distinguish the colours of the $\sigma$'s but only whether $\sigma_{x}$ is occupied or empty. Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$. Thus, we obtain 

@@

Moreover, because of the term $\delta_{\tau_{x},N}(1-c_{x})$, we can make vary the indices $c_{x}$ in the set $\{\delta_{\tau_{x},N},1\}$. Indeed, when $c_{x}=0$, the addend of the summation is non-vanishing only if $\tau_{x}=N$. Therefore, we obtain 

@@

\begin{remark}[Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution]
We argue as in the previous proof. For any $\bm{\tau}\in \Omega^{'}$ we have that 

@@

@@

We observe that for any $x\in \{1,\ldots,L\}$ the duality function \eqref{ElementsDualityMatrixChain_1} is
	d_{x}(\sigma_{x},\xi^{x}(\bm{\tau}))=\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}

@@

@@

 	\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
 where the above average is taken with respect to the non-equilibrium steady state of the process $\bm{\sigma}$. Equation \eqref{interpretation-PsiP} will be useful in Remark \ref{remark-NESS-invertingS1}. Given $\bm{\tau}$ as before, we can introduce the number of occupied sites $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$. We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present. Finally, we call 

@@

	\Psi^{'}(\bm{\tau})=&\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}_{\mu}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{\sigma_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution, in the sense described above. In particular, when the configuration $\bm{\tau}$ has at $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function. As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}. 
\subsection{Steady state}\label{appB}
In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}. This formula follows from Corollary \ref{Corollary-NESS-ABS}.
\begin{corollary}[Non-equilibrium steady state]
	The non-equilibrium steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
		|\Psi\rangle=\sum_{\bm{\tau}\in \Omega^{'}}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
	where, for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})\in \Omega^{'}$,
	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\right]
where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and are computed using \eqref{exactCorrelations}. 

@@

%%	\end{equation}

@@

	In the equilibrium case, when  $\alpha_{a}=\beta_{a}$ for all $a\in\{1,\ldots,N\}$ we obtain 
		\Psi(\bm{\tau})=\prod_{a=1}^{N}\beta_{a}^{\sum_{x=1}^{L}\delta_{\tau_{x},a}}
i.e. the product over sites of multinomial distribution with parameters $\nu=1$ and $\beta_{a}$. This is a direct consequence of the fact that $\beta_{N}=1-(\beta_{1}+\ldots+\beta_{N-1})$. 

@@

	We observe that if $\bm{\tau}$ has only non-empty occupations, i.e. $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then 
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
where the expectation is taken with respect to the $\mu$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$.

@@

	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}}
	The elements $\Psi(\bm{\tau})$ of the vector $|\Psi\rangle$ are the probabilities of having a certain configuration $\bm{\tau}\in \Omega^{'}$ in the non-equilibrium steady state, i.e.
		\Psi(\bm{\tau})=\langle \bm{\tau}|\Psi\rangle= \mu(\bm{\tau})\dt
 Therefore, they are given by the probability mass function of equation \eqref{implicit-mass-function} in Corollary \ref{Corollary-NESS-ABS}. 
\begin{remark}[Obtaining the steady state from the similarity $S_{1}$]\label{remark-NESS-invertingS1}
	 As a consequence of \eqref{S1-Inverse}, the non-equilibrium steady state $|\Psi\rangle$ can also be obtained by inverting the similarity transformation $S_{1}$. On a single site we have that 

@@

\textbf{Proof of \eqref{NESS-SSEP}:} the proof follows from \eqref{implicit-PSI-PSIp} and \eqref{PsiI-N2}. 

@@

	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu$. These average occupations evolve according to the master equation
	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]\dt

@@

	p=p_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}

@@

This can be proved by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries. %For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives

@@

\paragraph{Proof of duality}
We only prove duality for the bulk generator, since the boundary generators are the same as in Section \ref{Subsection-ss-nonI}. 

>>>>

Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square bracket, that is non-vanishing only if $\sigma_{x}=\tau_{x}$. On the other hand, if $\sigma_{x}=N$ the quantity $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}=1$. \\

@@

Indeed, considering the first and last equalities we have that: if $\tau_{x}=\sigma_{x}$, both sides are $1$; if $\tau_{x}\neq N$ and $\sigma_{x}=N$ both sides are $\beta_{\tau_{x}}$; while, in all other cases, both sides are $0$. 

@@

We observe that the argument of the summation above does not distinguish the colours of the $\sigma$'s but only whether, at each site $x$, $\sigma_{x}$ is occupied or empty. Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$. Thus, we obtain 

@@

Moreover, because of the term $(1-\delta_{\tau_{x},N})(1-c_{x})$ we can make the indices $c_{x}$ vary in the set $\{\delta_{\tau_{x},N},1\}$. Indeed, when $c_{x}=0$, this term is non-vanishing only if $\tau_{x}\neq N$. Therefore, we obtain 

@@

\subsubsection{Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
We argue similarly as in the Section \ref{correlation-section}. For any $\bm{\tau}\in \Omega^{'}$ we have that 

@@

\begin{align}\label{useful-InInterpretation}

@@

We observe that for any $x\in \{1,\ldots,L\}$
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
	%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
	%	1\qquad  &\text{if}\quad \tau_{x}= N
%	\end{cases}\dt
Indeed, we have that 
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}

@@

 Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation \ref{useful-InInterpretation}, we obtain 

@@

 	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
 This last equation will be used in Section \ref{appB}. {\color{blue}Given $\bm{\tau}$ as before, we can introduce the number of occupied sites $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$. We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present. Finally, we call 

@@

	\Psi^{'}(\bm{\tau})=&\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution, in the sense described above. In particular, when the configuration $\bm{\tau}$ has at $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function. As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}. }
\subsubsection{Steady state}\label{appB}
By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary \ref{Corollary-NESS-ABS}. Therefore, the vector $|\Psi\rangle$ is also determined. For the sake of completeness we show here that $|\Psi\rangle$ can be equivalently determined by inverting the similarity transformation $S_{1}$, using $|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ (cf. \eqref{S1-Inverse}). 
On a single site we have that 

@@

%%	\end{equation\end{corollary} 

@@

	Using equation \eqref{implicit-mass-function} with correlation computed in \eqref{exactCorrelations} in the equilibrium case ($\beta_{a}=\alpha_{a}$), we obtain 
		\Psi(\bm{\tau})=\prod_{a=1}^{N}\alpha_{a}^{\sum_{x=1}^{L}\delta_{\tau_{x},a}}
As it has to, this is the probability of the configuration $\bm{\tau}$ under the reversible measure \eqref{reversibleMeasure}, with site marginals distributed as $\text{Multinomial}(1,\alpha_{1},\ldots,\alpha_{N})$. 

@@

	We observe that, as a consequence of Section \ref{subsection-interpretationPSIp}, if $\bm{\tau}$ has only non-empty occupations, i.e. $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then 
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right]

@@

@@

\textbf{Proof of \eqref{NESS-SSEP}:} the proof follows from \eqref{implicit-PSI-PSIp} and from the coefficients $\Psi^{'}(\bm{\tau})$ computed in \eqref{PsiI-N2}. 

@@

	\rho_{a}(x,t)=\mathbb{E}_{\mu_{0}}\left[n_{a}^{x}(t)\right]
where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$. These average occupations evolve according to the master equation
	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu_{0}}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]\dt

@@

	p_{a}=p=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}

@@

This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.% Arguing as in Remark \ref{rem-rev}, conditions \eqref{cond-gen} become here
%	\alpha((N-2)\beta+\beta_{N})=\beta((N-2)\alpha+\alpha_{N})
%where $\alpha_{a}=\alpha_{b}=\alpha$ and $\beta_{a}=\beta_{b}=\beta$ for all $a,b\in \{1,\ldots,N-1\}$.%For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives

@@

\paragraph{Proof of duality:}
we only prove duality for the bulk generator, since the boundary generators are the same as in Section \ref{Subsection-ss-nonI}. 
